paper figures

### 2023-06-30 scRNAseq/paper_figures.Rmd
update

---
title: "20230627 paper figures"
output: 
  html_document:
    df_print: paged
    code_folding: hide
    toc: true
    toc_float: true
---

@@

- K456985_PBMC
- K783496_PBMC
- K693104_PBMC
- K955601_PBMC
- P1_1_PBMC (re-sequenced)
- P1_2_PBMC
- P3_1_PBMC
- P3_2_PBMC
- P8_1_PBMC
- P8_2_PBMC (re-sequenced)
- P22_1_PBMC
- P22_2_PBMC
- P23_1_PBMC
- P23_2_PBMC
- P25_1_PBMC
- P25_2_PBMC
- P27_1_PBMC
- P27_2_PBMC
- P28_1_PBMC
- P28_2_PBMC
- P22_P23_K783496_CD4
- P8_P3_K456985_CD4
- P27_P28_K693104_CD4
- P12_1_PBMC
- P12_2_PBMC
- P26_1_PBMC
- P26_2_PBMC
- K496398_PBMC
- P12_P26_K496398_CD4

>>>>

---
title: "paper figures"
output: 
  html_document:
    df_print: paged
    code_folding: hide
    toc: true
    toc_float: true
---

@@

- K456985_PBMC
- K783496_PBMC
- K693104_PBMC
- K955601_PBMC
- P1_1_PBMC
- P1_2_PBMC
- P3_1_PBMC
- P3_2_PBMC
- P8_1_PBMC
- P8_2_PBMC
- P22_1_PBMC
- P22_2_PBMC
- P23_1_PBMC
- P23_2_PBMC
- P25_1_PBMC
- P25_2_PBMC
- P27_1_PBMC
- P27_2_PBMC
- P28_1_PBMC
- P28_2_PBMC
- P22_P23_K783496_CD4
- P8_P3_K456985_CD4
- P27_P28_K693104_CD4
- P12_1_PBMC
- P12_2_PBMC
- P26_1_PBMC
- P26_2_PBMC
- K496398_PBMC
- P12_P26_K496398_CD4
